PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-28 paper.tex
Moving around figures

\begin{figure}
    \centering
    \includegraphics[width=0.55\linewidth]{setup-child-child.png}
    \hspace{1em}
    \includegraphics[width=0.4\linewidth]{child-child-env}
    \caption{The free play social interactions sandbox: two children interact in
    a free-play situation, by drawing and manipulating items on a touchscreen.}
    \label{fig|freeplay}
\end{figure}

@@

The experimental setup is presented in Fig.~\ref{fig|setup}.  The experimenter
stays in the room, visible to the child, during the whole experiment. When
requested by the nursery or school, another childminder (nursery/school staff)
can be present in the room. She/he is however asked not to step in during the
experiment.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\linewidth]{setup_child_child_top}
    %\hspace{1.5cm}
    %\includegraphics[width=0.4\linewidth]{setup_child_robot_top}
    %\caption{Experimental setup, child-child condition (left) and child-robot condition (right).}
    \caption{Experimental setup. Children are facing each other and sit on
    cushions. Each child wears a bright sport bib, either purple or yellow, to
    facilitate later identification.}
    \label{fig|setup}
\end{figure}

@@

The following acquisition procedure has been followed with all participants.

\newcommand{\tabitem}{~~\llap{\textbullet}~~}
    \begin{tabular}{@{}p{0.2\linewidth}p{0.8\linewidth}@{}}
\toprule
\bf Greetings                     & \tabitem explain the purpose of the study: showing robots how children play  \\
\emph{(about 5 min)}              & \tabitem briefly present a Nao robot -- the robot stands up, gives a short
                                    message (\emph{"Hello, I'm Nao. Today, I'll be watching you while you
                                    play and soon I'll be able to play with you. Is that alright?"}), and
                                    sits down. The robot is then put aside and does not intervene
                                    for the remaining of the experiment; \\
                                    %Condition B: "Hello, I'm Nao. Today I'll be playing with you. Exciting!")\\ 
                                  & \tabitem place children on cushions  \\ 
                                  & \tabitem give them the yellow/purple sport
                                  bibs and make sure their hair is tied \\ 
                                  & \tabitem complete demographics on the tablet \\
                                  & \tabitem remind the children that they can withdraw at anytime \\ \midrule
\bf Visual focus task             &  \\ 
\emph{(30 sec)}                   &  \\ \midrule
\bf Tutorial                      & explain how to interact with the game, ensure the children are confident with the manipulation/drawing \\ 
\emph{(1-2 min)}                  &  \\ \midrule
\bf Item placement game           &  \\
\emph{(5 to 10 min)}              &  \\ \midrule
\bf Freeplay task                 & \tabitem start the recording \\
\emph{(up to 40 min)}             & \tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
                                  like. If you run out of ideas, there's also an ideas box. For example, the first one is a
                                  zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
                                  anymore, just let me know."} \\
                                  & \tabitem let children play \\
                                  & \tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing                    &  \tabitem answer possible questions from the children \\
\emph{(about 2 min)}              & \tabitem give stickers as a thank you \\ \bottomrule
\end{tabular}

@@

The last part of the dataset consist in annotations of the
children's social behaviours. Some of these behaviours are automatically
computed and coded (mutual gaze, for instance), some are human-coded.

The annotations are integrated in the dataset as a timestamped datastream.

@@

We use the \emph{Social Communication Coding System} proposed by
Olswang~\etal\cite{olswang2006reliability}. It consists in 6 constructs
characterising social communication (table~\ref{table|sccs}).

@@

@@

The dataset is build with machine learning applications in mind, and
particularly, applications to socio-cognitive robotics.

Finally, the social setting (two players facing each other) implicitely invites
social interaction: onlooker play, for instance, is unlikely to be observed as
the children are physically engaged with the game and the other participant
(they are sitting in front of game, close to each other). The three higher forms
of social play listed by Parten (parallel play, associative play and cooperative
play) are however possible with this setup.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.55\linewidth]{setup_child_child_top}
    \hspace{1em}
    \includegraphics[width=0.4\linewidth]{child-child-env}
    \caption{The free-play social interactions sandbox: two children interact in
    a free-play situation, by drawing and manipulating items on a touchscreen.
    Children are facing each other and sit on cushions. Each child wears a
    bright sport bib, either purple or yellow, to facilitate later
    identification.}

    \label{fig|freeplay}
\end{figure}

@@

The experimental setup is visible in Fig.~\ref{fig|freeplay}, left.  The experimenter
stays in the room, visible to the child, during the whole experiment. When
requested by the nursery or school, another childminder (nursery/school staff)
can be present in the room. She/he is however asked not to step in during the
experiment.

@@

The following acquisition procedure has been followed with all participants. To
ease later identification, each child was given a colourful (purple or yellow)
sport bib to wear.

\newcommand{\tabitem}{~~\llap{\textbullet}~~}
    \begin{tabular}{@{}p{0.2\linewidth}p{0.8\linewidth}@{}}
\toprule
\bf Greetings                     & \tabitem explain the purpose of the study: showing robots how children play  \\
\emph{(about 5 min)}              & \tabitem briefly present a Nao robot: the robot stands up, gives a short
                                    message (\emph{"Hello, I'm Nao. Today, I'll be watching you while you
                                    play and soon I'll be able to play with you. Is that alright?"}), and
                                    sits down. The robot is then put aside and does not intervene
                                    for the remaining of the experiment \\
                                    %Condition B: "Hello, I'm Nao. Today I'll be playing with you. Exciting!")\\ 
                                  & \tabitem place children on cushions \\ 
                                  & \tabitem give them the yellow/purple sport
                                  bibs and make sure their hair is tied \\ 
                                  & \tabitem complete demographics on the tablet \\
                                  & \tabitem remind the children that they can withdraw at anytime \\ \midrule
        \bf Visual focus task             &  \emph{}\\ 
\emph{(30 sec)}                   &  \\ \midrule
\bf Tutorial                      & explain how to interact with the game, ensure the children are confident with the manipulation/drawing \\ 
\emph{(1-2 min)}                  &  \\ \midrule
\bf Item placement game           &  \\
\emph{(5 to 10 min)}              &  \\ \midrule
\bf Freeplay task                 & \tabitem start the recording \\
\emph{(up to 40 min)}             & \tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
                                  like. If you run out of ideas, there's also an ideas box. For example, the first one is a
                                  zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
                                  anymore, just let me know."} \\
                                  & \tabitem let children play \\
                                  & \tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing                    &  \tabitem answer possible questions from the children \\
\emph{(about 2 min)}              & \tabitem give stickers as a thank you \\ \bottomrule
\end{tabular}

@@

The last part of the dataset consist in annotations of the
children's social behaviours. Some of these behaviours are automatically
computed and coded (mutual gaze, for instance), some are human-coded.
The annotations are integrated in the dataset as a timestamped datastream.

@@

We use the \emph{Social Communication Coding System} proposed by
Olswang~\etal\cite{olswang2006reliability}. It consists in 6 constructs
characterising social communication (Table~\ref{table|sccs}).

@@

%CERE: this didn't table for me?

@@

The dataset is built with machine learning applications in mind, and
particularly, applications to socio-cognitive robotics.

Finally, the social setting (two players facing each other) implicitly invites
social interaction: onlooker play, for instance, is unlikely to be observed as
the children are physically engaged with the game and the other participant
(they are sitting in front of game, close to each other). The three higher forms
of social play listed by Parten (parallel play, associative play and cooperative
play) are however possible with this setup.
